TODO: A Survey of StarCraft AI Techniques

### 2012-02-28 survey.tex
competition part started

\section{The Starcraft AI Competition}\label{sec:competition}

{\color{blue}
Here describe the results obtained in the competition comparing the bots.
}

>>>>

\section{Recent Starcraft AI Competitions}\label{sec:competition}

{\color{magenta}

\subsection{CIG 2011}
\label{sec:cig2011}

An initial attempt to run a StarCraft tournament at the Computational
Intelligence in Games conference 2010 suffered from technical problems.
These mainly stemmed from the desire to use evolved, largely untested
maps which proved to look interesting but made the submitted bots crash
so often that it would have been unjustifiable to announce a winner.

At the CIG 2011, the tournament was therefore run with a (secret) selection
of maps used in league play. It was organized by Tobias Mahlmann and Mike
Preuss and attracted 10 bots.

\begin{table*}[htb]
\caption{Bracket A results at CIG 2011, 
qualified for the final round: UAlbertaBot and Skynet.}
\label{tab:correlations}
\begin{small}
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
Crashes & games & bot	& wins\\ \hline
0 &	 40 &	 UAlbertaBot &	 33\\
1 &   40 &	 Skynet	  &  31\\
2 &	 40 &	 AIUR	  &  24\\
1 &	 40 &	 Nova	  &  8\\
0 &	 40 &	 LSAI	  &  4\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

Bracket B

Crashes	 Games	 Bot	 Wins
12	 40	 Xelnaga	 25
3	 40	 BroodwarBotQ	 23
0	 40	 BTHAI	 23
17	 40	 Protoss Beast Jelly	 17
0	 40	 EvoBot	 12
As BroodwarBotQ and BTHAI have the same number of wins, their direct encounter is evaluated which accounted 6 : 4 for the BroodwarBotQ.

Qualified for the final round: Xelnaga and BroodwarBotQ. Note that all qualified bots play Protoss.
Maps used for the first round: (2)MatchPoint 1.3, (4)Fighting Spirit 1.3, iCCupdestination 1.1, iCCup gaia, iCCup great barrier reef

Final Round

The final round was played in a similar mode as each of the first round brackets, using another set of 5 maps (see below), resulting in 30 games for each bot.

Crashes	 Games	 Bot	 Wins
0	 30	 Skynet	 26
0	 30	 UAlbertaBot	 22
3	 30	 Xelnaga	 11
2	 30	 BroodwarBotQ	 1

Here describe the results obtained in the competition comparing the bots.
}
